MacLeish

### 2016-04-10 README.Rmd

```{r, eval=FALSE}
whately <- macleish %>%
  tbl("whately")
whately %>%
  mutate(the_year = strftime('%Y', when)) %>%
  group_by(the_year) %>%
  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
orchard <- macleish %>%
  tbl("orchard")
orchard %>%
  mutate(the_year = strftime('%Y', when)) %>%
  group_by(the_year) %>%
  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
```

```{r, eval=FALSE, fig.width = 7, fig.height = 5, message=FALSE}
daily <- whately %>%
  mutate(the_date = date(when)) %>%
  group_by(the_date) %>%
  summarize(N = n(), avgTemp = mean(Temp_C_Avg)) %>%
  collect()
library(ggplot2)
ggplot(data = daily, aes(x = as.Date(the_date), y = avgTemp)) +
  geom_point() + geom_smooth()
```

>>>>

```{r, eval=FALSE}
whately <- macleish %>%
  tbl("whately")
whately %>%
  mutate(the_year = strftime('%Y', when, 'unixepoch')) %>%
  group_by(the_year) %>%
  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
orchard <- macleish %>%
  tbl("orchard")
orchard %>%
  mutate(the_year = strftime('%Y', when, 'unixepoch')) %>%
  group_by(the_year) %>%
  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
```

```{r, eval=FALSE, fig.width = 7, fig.height = 5, message=FALSE}
daily <- whately %>%
  mutate(the_date = date(when, 'unixepoch')) %>%
  group_by(the_date) %>%
  summarize(N = n(), avgTemp = mean(Temp_C_Avg)) %>%
  collect()
library(ggplot2)
ggplot(data = daily, aes(x = as.Date(the_date), y = avgTemp)) +
  geom_point() + geom_smooth()
```
